\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-28 doc/sui14/iteration3.tex
iteration3.tex: his->their
use 0.95 for all figures

In the learning stage, the user scans over the targets, and the system attains
the absolute orientation of each device from IR and motion sensors. From this
information it can abstract out their relative positions and build an {\em
adjacency map}.

This absolute orientation cannot be applied to all indoor environments, since
the user’s movements through the space could change the relationships between
targets. However, with the constraint that the targets are spread around the
periphery, their relative orientations are stable (see
Figure~\ref{fig:third_principle}).

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_principle.png}
\caption{This illustrates that the change of a user's absolution position
doesn't change the relative relationship of physical targets.}
\label{fig:third_principle}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique.pdf}
\caption{Our third technique learned each target's absolute orientation and
construct the adjacency map. During the {\em refinement} stage, the prediction
is based on relative changes to a reference point.}
\label{fig:third_technique}
\end{figure}

After the map is created, the user can hold down on the touchpad to enter a
quasi-mode for refinement. In this quasi-mode, one device lights up at a time.
When the user turns his head in the direction of another device, the light
switches to that device. Therefore, the user can move between devices one at a
time with slight head movements. We implement this interaction by calculating
the user's direction of motion using a low-passed history of sensor
measurements and searching through the adjacency map for the nearest device in
that direction.

>>>>

In the learning stage, as the user scans over targets in their normal use, the
system attains the absolute orientation of each device from IR and motion
sensors. From this information it can abstract out their relative positions and
build an {\em adjacency map}. This process is transparent to the user, and the
map can be built without an explicit calibration phase.

This absolute orientation cannot be applied to all indoor environments, since
the user's movements through the space could change the relationships between
targets. However, with the constraint that the targets are spread around the
periphery, their relative orientations are stable (see
Figure~\ref{fig:third_principle}).

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/third_principle.png}
\caption{This illustrates that the change of a user's absolution position
doesn't change the relative relationship of physical targets.}
\label{fig:third_principle}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/third_technique.pdf}
\caption{Our third technique learned each target's absolute orientation and
construct the adjacency map. During the {\em refinement} stage, the prediction
is based on relative changes to a reference point.}
\label{fig:third_technique}
\end{figure}

After the map is created, the user can hold down on the touchpad to enter a
quasi-mode for refinement. In this quasi-mode, one device lights up at a time.
When the user turns their head in the direction of another device, the light
switches to that device. Therefore, the user can move between devices one at a
time with slight head movements. We implement this interaction by calculating
the user's direction of motion using a low-passed history of sensor
measurements and searching through the adjacency map for the nearest device in
that direction.
